---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Flexible Cycle threshold modelling

[![R-CMD-check](https://github.com/seabbs/epict/workflows/R-CMD-check/badge.svg)](https://github.com/seabbs/epict/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/seabbs/epict/branch/main/graph/badge.svg)](https://app.codecov.io/gh/seabbs/epict?branch=main)

[![MIT
license](https://img.shields.io/badge/License-MIT-blue.svg)](https://github.com/epiforecasts/epict/blob/master/LICENSE.md/)
[![GitHub contributors](https://img.shields.io/github/contributors/seabbs/epict)](https://github.com/seabbs/epict/graphs/contributors) 


Flexible piecewise modelling of cycle thresholds with adjustment for varying intercepts and linear scales.

## Installation

### Installing the package

Install the unstable development from GitHub using the following, 

```{r, eval = FALSE}
remotes::install_github("seabbs/epict", dependencies = TRUE)
```

### Installing CmdStan

If you don't already have CmdStan installed then, in addition to installing `epict`, it is also necessary to install CmdStan using CmdStanR's 
`install_cmdstan()` function to enable model fitting in `epict`. A suitable C++ toolchain is also required. Instructions are provided in the [_Getting started with
CmdStanR_](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) vignette. See the [CmdStanR documentation](https://mc-stan.org/cmdstanr/) for further details and support. 

```{r, eval = FALSE}
cmdstanr::install_cmdstan()
```

## Quick start


### Package

As well as `epict` this quick start makes use of `data.table` and `ggplot2` which are both installed when `epict` is installed.

```{r}
library(epict)
library(data.table)
library(ggplot2)
```

### Data

### Data preprocessing and model specification

### Model fitting

### Results

## Citation

If using `epict` in your work please consider citing it using the following,

```{r, echo = FALSE}
citation("epict")
```

## How to make a bug report or feature request

Please briefly describe your problem and what output you expect in an [issue](https://github.com/seabbs/epict/issues). If you have a question, please don't open an issue. Instead, ask on our [Q and A page](https://github.com/seabbs/epict/discussions/categories/q-a).

## Contributing

We welcome contributions and new contributors! We particularly appreciate help on priority problems in the [issues](https://github.com/seabbs/epict/issues). Please check and add to the issues, and/or add a [pull request](https://github.com/seabbs/epict/pulls).

If interested in expanding the functionality of the underlying model note that `epict` allows users to pass in their own models meaning that alternative parameterisations may be easily tested within the package infrastructure. Once this testing has been done alterations that increase the flexibility of the package model and improves its defaults are very welcome via pull request or other communication with the package authors.

## Code of Conduct
  
Please note that the `epict` project is released with a [Contributor Code of Conduct](https://samabbott.co.uk/epict/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
